Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-24 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Circular Cross-Section Results}

\section{Parameter Exploration}
Include the graphs showing critical buckling strain as a function of parameters.\\
\mf{Add figures for the diagonal}\\
\mf{Add figure for $\lambda$ exploration}\\
\mf{Make sure to include this analysis for both, rectangular cross-section and circular cross-section}\\
\mf{Write this section}
\subsection{Cylindrical Cross Section}
\subsection{Rectangular Cross Section}

>>>>

\section{Circular Cross-Section Results}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\linewidth]{SFig7.pdf}
	\caption{{\bf Circular Cross Section Results.} The color of the lines correspond to it's respective design color below the plots. (a) Shows the linear elastic stiffness of the different designs as a function of the loading angle. All structures except for the design without diagonal reinforcement have the same stiffness. (b) Shows the critical buckling strain for varying loading angle. For all angles, Design A outperforms other diagonally reinforced designs. These results show that the two diagonal benefit persists beyond a particular beam cross-section design.}

	\label{CircularCrossSection}
\end{figure}
\section{Parameter Exploration}
Include the graphs showing critical buckling strain as a function of parameters.\\
\mf{Add figures for the diagonal}\\
\mf{Add figure for $\lambda$ exploration}\\
\mf{Make sure to include this analysis for both, rectangular cross-section and circular cross-section}\\
\mf{Write this section}
\subsection{Rectangular Cross Section}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig8.pdf}
	\caption{{\bf Circular Cross Section Results.} gsdfgs}
	\label{CircularCrossSectionParameter}
\end{figure}

\subsection{Cylindrical Cross Section}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig9.pdf}
	\caption{{\bf Circular Cross Section Results.} gsdfgs}
	\label{SquareCrossSectionParameter}
\end{figure}
